\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-27 introduction.tex
address/reply to comments in intro

\item We present the first language design that enables extensible
metatheory mechanization in a higher-order, dependent type theory with
inductive types (\cref{sec:lang-design}).
The language design reconciles the expressiveness enabled by
family polymorphism with the exactness of a proof assistant,
while retaining an idiomatic programming style.

@@

\item We capture the essence of the new language mechanism formally by extending
Martin–Löf type theory with family polymorphism and extensible inductive
types (\cref{sec:metatheory}).
We derive strong meta\-theoretical results including consistency and
canonicity.
We also formalize the translation implemented by the Coq plugin.

>>>>

\item We present, to our knowledge, the first\EDJ{Are you sure? This claim is so bold.}\YZreply{Is there any previous language designs in this space?} language design that enables extensible
metatheory mechanization in a higher-order, dependent type theory with
inductive types (\cref{sec:lang-design}).
The language design reconciles the expressiveness enabled by
family polymorphism with the rigor of a proof assistant,
while retaining an idiomatic programming style.

@@

\item We capture the essence of the new language mechanism formally by extending
Martin–Löf type theory with family polymorphism and extensible inductive
types (\cref{sec:metatheory}).
We derive foundational meta\-theoretical results including consistency
and canonicity.
%\EDJ{I will suggest use ``foundational'' instead. Sterling at some places say canonicity is the most basic meta-theoretical property.}
We also formalize the translation implemented by the Coq plugin.
